Höglinger et al. 2017

### 2025-01-16 IndividualStudies/DH_2017.qmd
Actual EOD

DH_2017_data_long <- read.csv("DataTables/DH_PNAS_2017_long.csv")

DH_2017_data_long$name <- factor(pull(DH_2017_data_long, name), ordered = TRUE, levels = c("Sph", "FA", "DAG"))

@@

heatmap <- DH_2017_data_long |>
  ggplot(aes(y = id, x = name)) +
  theme(panel.border = element_rect(color = NA, fill = "grey25")) +
  geom_tile(aes(fill = value, text = paste0("Gene name: ", gene_name, '\n', "Lipid Probe:", name, "\n", "PSM: ", value))) +
  scale_fill_gradientn(colors = c("grey95", "purple", "orange"),
  values = scales::rescale(c(0, 10, 25))) +
  ylab("Gene") +
  xlab("Lipid Probe") +
  theme_minimal() +
  theme(text = element_text(family = "serif")) +

  theme(legend.title = element_text(size = 12, face = "bold")) +
  theme(axis.title = element_text(size = 12, face = "bold")) +
  theme(legend.text = element_text(size = 12))

>>>>

DH_2017_data_long <- read.csv("DataTables/DH_PNAS_2017_long.csv") |>
  mutate(PSM = value, sample = name) |>
  group_by(gene_name, sample) |>
  summarise(PSM = mean(PSM, na.rm = TRUE), .groups = "drop") |>
  distinct()

DH_2017_data_long$sample <- factor(pull(DH_2017_data_long, sample), ordered = TRUE, levels = c("Sph", "FA", "DAG"))

heatmap <- DH_2017_data_long |>
  ggplot(aes(y = gene_name, x = sample)) +
  theme(panel.border = element_rect(color = NA, fill = "grey25")) +
  geom_tile(aes(fill = PSM, text = paste0("Gene name: ", gene_name, '\n', "Lipid Probe:", sample, "\n", "PSM: ", PSM))) +
  scale_fill_gradientn(colors = c("grey95", "purple", "orange"),
  values = scales::rescale(c(0, 10, 25))) +
  ylab("Gene") +
  xlab("Lipid Probe") +
  theme_minimal() +
  theme(text = element_text(family = "serif")) +
  theme(legend.title = element_text(size = 12, face = "bold")) +
  theme(axis.title = element_text(size = 12, face = "bold")) +
  theme(legend.text = element_text(size = 12))

@@
